\section{Activities} \label{sec:activities}

\begin{enumerate}
  \item{\textbf{Phase I: Review of vulnerabilities in RESTful APIs}

    \begin{enumerate}
      \item Review of the most recent surveys about vulnerabilities in RESTful APIs and mutation testing in APIs according to the research questions.
      \item Identify the objective data sources to be used in the research.
      \item Select of the scope of the vulnerabilities to be tested.
      \item Identify elements of these selected vulnerabilities Restful APIs.
      \item Selection of the software vulnerabilities in terms of configuration of API services.
      \item Analysis of the elements of the selected vulnerabilities in RESTful APIs.
      \item Analysis of the strategies used to mitigate these vulnerabilities.
      \item Determine the elements used in software testing for the assessment of these vulnerabilities
  \end{enumerate}}

  \item{\textbf{Phase II: Description of the mutation operators}

    \begin{enumerate}
      \item Describe how mutation is applied to introduce vulnerability.
      \item Creation of data generation cases for introducing vulnerabilities. 
      \item Define the types of mutation operators will introduce vulnerabilities in the configuration files.
      \item Determine how to apply modifications to the source code to apply the mutation operator.
      \item Describe the different scenarios to apply the mutation operators.
      \item Identify the relevant tests elements to be evaluated.
      \item Review the mutation operators to determine the theoretical coverage and redundancy metrics.
      \item Modify the mutation operators to improve the coverage and redundancy metrics.
  \end{enumerate}}

  \item{ \textbf{Phase III: Prototype implementation and testing}

    \begin{enumerate}
    \item Generate test cases to verify the functionality of the mutation operators.
    \item Study a mutation testing engine to introduce the mutation operators.
    \item Code the mutation operators in the mutation testing engine.
    \item Refactor the code to improve the quality and maintainability of the code.
  \end{enumerate}}

\item{ \textbf{Phase IV: Evaluation of the mutation operators}

  \begin{enumerate}
    \item Select a set of RESTful API services to evaluate the mutation operators.
    \item Evaluate the factors of vulnerability present, complexity of the API and their relevance for the evaluation of the mutation operators.
    \item Execute the security tests in the selected API services to review the detection of vulnerabilities.
    \item Apply the mutation operators in the selected API services.
    \item Analyze the coverage and redundancy metrics of the mutation testing process considering the metrics of mutation coverage, fault detection, execution time, false positive rate and mutation score.
  \end{enumerate}}
  \item {Write the final report of the research.}
\end{enumerate}

